---
title: "Data Science, Police Accountability, and Community Engagement Research Lab"
section-divs: false
#page-layout: full
toc: false
anchor-sections: false
bibliography: references.bib
csl: diabetologia.csl
---

The Data Science, Police Accountability, and Community Engagement (DSPACE) Research Lab partners with communities to work towards data-informed police accountability. Our group originated as the Small Town Policing Accountability (SToPA) Lab within the [Institute for Quantitative Study of Inclusion, Diversity, and Equity](https://qsideinstitute.org/) (QSIDE Institute). The SToPA Lab was developed in 2021 by a group of data scientists, social justice activists, and statisticians in response to discriminatory practices within the Williamstown, MA police department @cohen2020. In Spring 2024, members of the SToPA Lab formed this new DSPACE Research Lab focused on communities of all sizes and as the research-intensive branch in the realm of police accountability. Our team of mathematicians, statisticians, and data scientists collaborates with community members and organizations to answer challenging questions about patterns in policing. Our endeavor is to make a direct and meaningful impact with the public and to contribute to scholarly research at the intersection of data science/statistics and policing.

The DSPACE Research Lab is supported by the University of Minnesota’s Institute for Advanced Study as a Research and Creative Collaborative. 
<br>
</br>

## Lab Contributors

<style>
.card-grid {
display: flex;
flex-wrap: wrap;
gap: 10px;
justify-content: center;
}

.card {
width: 150px;
border: 0px solid #ccc;
border-radius: 5px;
overflow: hidden;
text-decoration: none;
color: inherit;
transition: box-shadow 0.2s ease;
}

.card-content p {
  font-size: 12px;
  margin: 0;
}
.card-content h5 {
  font-size: 16px
}

.card:hover {
box-shadow: 0 4px 12px rgba(0,0,0,0.1);
}

.card img {
width: 100%;
height: 150px;
object-fit: cover;
}

.card-content {
padding: 15px;
}
</style>

<div class="card-grid">
<!---->
<a class="card" href="https://clairekelling.com/index.html" target="_blank">
<img src=files/images/Claire.jpg alt="Image 1">
<div class="card-content">
<h5>Claire Kelling</h5>
<p>Assistant Professor of Statistics, Carleton College</p>
</div>
</a>
<!---->
<a class="card" href="https://www.arianamendible.com/" target="_blank">
<img src=files/images/Ariana.jpg alt="Ariana Mendible">
<div class="card-content">
<h5>Ariana Mendible</h5>
<p>Assistant Professor of Mathematics and Data Science, Seattle University</p>
</div>
</a>
<!---->
<a class="card" href="https://www.alexwiedemann.online/" target="_blank">
<img src=files/images/Alex.jpg alt="Alex Wiedemann">
<div class="card-content">
<h5>Alex Wiedemann</h5>
<p>Assistant Professor of Mathematics and Computational Data Science,  Hamline University</p>
</div>
</a>
<!---->
<a class="card" href="https://www.tmarrinan.com/" target="_blank">
<img src=files/images/Tim.jpg alt="Tim Marrinan">
<div class="card-content">
<h5>Tim Marrinan</h5>
<p>Data Scientist, <br> PhD Mathematics</p>
</div>
</a>
<!---->
<a class="card" target="_blank">
<img src=files/images/rwglogo.jpg alt="RWG">
<div class="card-content">
<h5>Reinvestigation Workgroup</h5>
<p>A Minnesota-based investigation team that reinvestigates police killings</p>
</div>
</a>
<!---->
<a class="card" target="_blank">
<img src=files/images/Will.jpg alt="Will Asinger">
<div class="card-content">
<h5>Will Asinger</h5>
<p>PhD Student, Biostatistics and Health Data Science, University of Minnesota</p>
</div>
</a>
<!---->
<a class="card" target="_blank">
<img src=files/images/Jesse.jpg alt="Jesse Loi">
<div class="card-content">
<h5>Jesse Loi</h5>
<p>Student Researcher, MS Data Science, Seattle University</p>
</div>
</a>
<!---->
<a class="card" target="_blank">
<img src=files/images/Maren.jpg alt="Maren Rusk">
<div class="card-content">
<h5>Maren Rusk</h5>
<p>Student Researcher, Statistics and Politics, Pomona College</p>
</div>
</a>
<!---->
<a class="card" target="_blank">
<img src=files/images/Mia.jpg alt="Mia (Cong) Wang">
<div class="card-content">
<h5>Mia (Cong) Wang</h5>
<p>Student Researcher, BS Mathematics & Statistics '25, Carleton College</p>
</div>
</a></div>
<!---->
<!--<a class="card" href="https://example.com/6" target="_blank">
<img src="https://via.placeholder.com/250x150" alt="Image 6">
<div class="card-content">
<h5>Card Title 6</h5>
<p>Description for card 6.</p>
</div>
</a>-->
</div>


## Recent Developments
```{r, echo = F, message = F, waring = F}
library(googlesheets4)
library(dplyr)

# Replace with your developments sheet ID
developments_sheet_id <- "17PethTSGMLFswtIZWl1ZYZYZnH-YocWK2X3CvTDssjU"

gs4_auth()  # authenticate for Google sheets

devs <- read_sheet(developments_sheet_id, 
                   sheet = "Sheet1") %>%  
  filter(!is.na(short_description) & short_description != "") %>%
   arrange(desc(date))

# Badge color per type
type_colors <- c(
  community   = "#c48a3a",
  publication = "#4a7fa5",
  talk        = "#7a9e6e",
  media       = "#9b6fa5",
  service     = "#5a9e9e",
  student     = "#c46a6a",
  update      = "#6a7a9e"
)

type_labels <- c(
  community   = "Community",
  publication = "Publication",
  talk        = "Talk",
  media       = "Media",
  service     = "Service",
  student     = "Student",
  update      = "Update"
)

make_feed_item <- function(i) {
  type    <- tolower(trimws(devs$category[i]))
  color   <- ifelse(type %in% names(type_colors), 
                    type_colors[type], "#888")
  label   <- ifelse(type %in% names(type_labels), 
                    type_labels[type], devs$category[i])
  date_fmt <- format(as.Date(devs$date[i]), "%b %Y")
  title_html <- paste0('<span class="feed-title">',
                       devs$short_description[i], '</span>')
  desc_html <- if (!is.na(devs$long_description[i]) &&
                   devs$long_description[i] != "") {
    paste0('<p class="feed-desc">', devs$long_description[i], '</p>')
  } else ""
  paste0(
    '<div class="feed-item">',
      '<div class="feed-left">',
        '<div class="feed-dot" style="background-color:', 
    color, '"></div>',
        '<div class="feed-line"></div>',
      '</div>',
      '<div class="feed-right">',
        '<div class="feed-meta">',
          '<span class="feed-badge" style="background-color:', 
    color, '">', label, '</span>',
          '<span class="feed-date">', date_fmt, '</span>',
        '</div>',
        title_html,
        desc_html,
      '</div>',
    '</div>'
  )
}
```


```{r, echo = F}
#| results: asis

cat('<div class="feed-container">\n')
for (i in seq_len(nrow(devs))) {
  cat(make_feed_item(i))
  cat("\n")
}
cat('</div>\n')
```

<style>
.feed-container {
  margin-top: 1rem;
  max-width: 720px;
}
.feed-item {
  display: flex;
  gap: 1rem;
  margin-bottom: 0;
}
.feed-left {
  display: flex;
  flex-direction: column;
  align-items: center;
  width: 16px;
  flex-shrink: 0;
}
.feed-dot {
  width: 12px;
  height: 12px;
  border-radius: 50%;
  flex-shrink: 0;
  margin-top: 0.35rem;
}
.feed-line {
  width: 2px;
  flex: 1;
  background-color: #e0e0e0;
  margin-top: 4px;
}
.feed-item:last-child .feed-line {
  display: none;
}
.feed-right {
  padding-bottom: 1.4rem;
  flex: 1;
}
.feed-meta {
  display: flex;
  align-items: center;
  gap: 0.6rem;
  margin-bottom: 0.3rem;
}
.feed-badge {
  font-size: 0.72rem;
  font-weight: 600;
  color: #fff;
  border-radius: 20px;
  padding: 0.1rem 0.55rem;
  text-transform: uppercase;
  letter-spacing: 0.04em;
}
.feed-date {
  font-size: 0.8rem;
  color: #888;
}
.feed-title {
  font-size: 0.95rem;
  font-weight: 600;
  color: #222;
  text-decoration: none;
  display: block;
  line-height: 1.4;
}
a.feed-title:hover {
  color: #4a7fa5;
  text-decoration: underline;
}
.feed-desc {
  font-size: 0.875rem;
  color: #555;
  margin: 0.25rem 0 0 0;
  line-height: 1.5;
}
</style>

